% !TEX encoding = UTF-8
% !TEX TS-program = pdflatex
% !TEX spellcheck = en-US

\documentclass[10pt,a4paper,colorlinks,linkcolor=true]{moderncv}

%************************************************
%************************************************
% Import packages
%************************************************
%************************************************
\usepackage{newpxtext} % Use Palatino font
\usepackage[utf8]{inputenc} % This are for non-ASCII letters, like accents
\usepackage[T1]{fontenc} % This are for non-ASCII letters, like accents
\usepackage[scale=0.85]{geometry} % This is for shortening/handling the margins
\usepackage{eurosym} % This is useful for the € symbol
\usepackage{soul} % Hyphenation for letterspacing, underlining
\usepackage{etoolbox} % To use \patchcmd for redefining commands

%************************************************
%************************************************
% Moderncv configuration
%************************************************
%************************************************
\moderncvcolor{blue} % Define the primary color of the cv
\moderncvicons{awesome} % Use the moderncv icons for socials and addresses
\moderncvhead{3} % Body of banking style
\moderncvbody{1} % Body of casual style
\moderncvfoot{1} % Footer of casual style

%************************************************
%************************************************
% Moderncv fix header:
% - full text width
% - add space after name-title and before addresses
%************************************************
%************************************************
\makeatletter
\patchcmd{\makehead} % <cmd>
  {0.8\textwidth} % <search>
  {\textwidth} % <replace>
  {} % <success>
  {} %<failure>
\patchcmd{\makehead} % <cmd>
  {\ifthenelse{\equal{\@title}{}}{}{\titlestyle{~|~\@title}}} % <search>
  {\ifthenelse{\equal{\@title}{}}{}{\titlestyle{~|~\@title}\vspace{0.5\baselineskip}}} % <replace>
  {} % <success>
  {} % <failure>
\makeatother

%************************************************
%************************************************
% Moderncv fix footer:
% - full text width as it happens for the header
%************************************************
%************************************************
\renewcommand*{\recomputefootlengths}{%
  \setlength{\footwidth}{\textwidth}} % original: 0.8\textwidth

\recomputelengths

\setlength{\hintscolumnwidth}{1.5cm} % The left side is 1.5 cm large


%************************************************
%************************************************
% Create new commands
%************************************************
%************************************************

% Create command for splitting being able to span text on multiple rows
\newcommand{\cvlanguagesplit}[3]{%
  \cvlanguage{#1}{\parbox[t]{\maincolumnwidth}{#2}}{#3}%
}

% Create command for publications:
% - right side: first row with title, second row with authors
% - left side: first row with conference name, second row with doi link
\newcommand*{\cvpublication}[5]{%
  \cvline{#1}{ % #1 is the year number
    \begin{minipage}[t]{.80\maincolumnwidth}\emph{#2}\\ % #2 is the paper title
      \footnotesize{\color{gray} #4} % #4 is the list of authors
    \end{minipage}
    \hfill
    \begin{minipage}[t]
      {0.19\maincolumnwidth}\raggedleft\footnotesize\textbf{#3}\\ % #3 is the conference
      \scriptsize{#5} % #5 is the doi link
    \end{minipage}
  }
}

\renewcommand*{\sectionfont}{\Large\upshape}
\renewcommand*{\hintfont}{\footnotesize\sffamily}

\newcommand{\cvlink}[2]{\href{#1}{\ul{#2}}}
\newcommand{\doilink}[2]{\href{#1}{\texttt{\ul{#2}}}}


\newcommand{\danieleauthor}{\textbf{\textcolor{black}{D. Foroni}}}


\nopagenumbers{} % Remove number of pages

%************************************************
%************************************************
% Moderncv header information
%************************************************
%************************************************
\firstname{Daniele}
\familyname{Foroni}
\title{Ph.D.}
% \address{street and number}{postcode city} % optional, remove / comment the line if not wanted
% \phone{+39 348 068 7589} % optional, remove / comment the line if not wanted
% \mobile{+39 348 068 7589} % optional, remove / comment the line if not wanted
% \photo[64pt]{picture} % optional, remove / comment the line if not wanted
\email{daniele.foroni@gmail.com} % optional, remove / comment the line if not wanted
\homepage{forons.github.io} % optional, remove / comment the line if not wanted
\social[twitter]{forons}
\social[github]{forons}
\social[linkedin]{danieleforoni}


%************************************************
%************************************************
% Begin document
%************************************************
%************************************************

\begin{document}
\hypersetup{urlcolor=black}

\makecvtitle
\pagestyle{empty} % Removes footer for the first page
\setlength{\parskip}{0.4ex}

\vspace*{-5mm}

Senior Data Engineer and Senior Data Scientist with 5+ years of experience in designing, scaling, and deploying data processing pipelines in production, as well as in creating models and optimization algorithms in the Smart Cities context. Most recently developed an optimization algorithm for traffic light management that reduces of up to 20 \% the driving time.
% My research focuses on Big Data Management and Analysis, particularly to the applications where they can improve the current systems.
% Currently, I am working on managing traffic data from smart cities to optimize the traffic lights, predicting and managing congestion, and reducing the traffic in certain area through regional technologies.
% During the PhD, I studied how to improve the quality of the data by considering the involved application and the optimization metrics the user has in mind, as well as the intrinsic value of the data.
% My research focuses on Big Data Management and Analysis, particularly on data quality assessment for improving the current system.
% To do so, I built and published about F4U, a framework for measuring the impact of the noise on the accuracy of the results, and Moira, a system to dynamically allocate the appropriate amount of resources to optimize the goal metric defined by the user.


%************************************************
%************************************************
\section{Work Experience}
%************************************************
%************************************************

\cventry{From 2019 Aug--\emph{Now}}{Senior Big Data Research Engineer}{Huawei MRC (Munich Research Center)}{Munich}{Germany}{
  Research and develop Big Data technologies with special focus on real-time and streaming technologies, and techniques for traffic management optimization in smart city environments. I create algorithms for traffic optimization, which reduced up to 20 \% the driver delay, and for anomaly discovery in traffic patterns. Moreover, I am in charge for delivering to product the features developed by the whole team. I am also the codebase, CI, and server maintainer.
}


\cventry{From 2018 Oct--\emph{Now}}
  {CTO and Full-Stack Developer}
  {\cvlink{https://www.iohub.eu/}{IOHub}}
  {Rovereto}{Italy}
  {Start-up that targets privacy-aware solutions for both citizens and businesses about the Italian electronic invoicing system. CEO: \cvlink{https://www.linkedin.com/in/gianmaria-conti-38303712/}{Gianmaria Conti}}

\cventry{2017--2018}
  {Research Engineer Intern}
  {Huawei ERC}
  {Munich}{Germany}
  {Visiting researcher working on dynamic rescheduling resources for streaming queries in a distributed environment based on the goal metrics defined by the user. Advisors: \cvlink{https://www.linkedin.com/in/stefano-bortoli/}{Stefano Bortoli} and \cvlink{https://www.linkedin.com/in/radu-tudoran-37545643/}{Radu Tudoran}}

\cventry{2016--2017}
  {Data Scientist}
  {University of Trento and Saidea SRL}
  {Trento}{Italy}
  {Development of XplainBox, an industrial tool that reads and stores data in a streaming fashion, and on it performs analyses and applies ML algorithms.}

\cventry{2014 Feb--Nov}
  {Data Engineer Intern}
  {Engineering Tributi SPA}
  {Trento}{Italy}
  {Development of an entity resolution tool that, with a set of rules, compares similar entities, avoiding meaningless comparisons. Advisor: \cvlink{https://www.linkedin.com/in/nicolamezzetti/}{Nicola Mezzetti}}



%************************************************
%************************************************
\section{Education}
%************************************************
%************************************************

\cventry{2014--2019}
  {Ph.D. in Computer Science}
  {University of Trento}{Italy}
  {\textit{Program funded by \cvlink{https://www.telecomitalia.com/en/innovation/open-innovation/tim-open-labs.html}{SkilLab - TIM (Telecom Italia)}}}
  {Thesis: \emph{Putting Data Quality in Context: How to generate more accurate analyses}. Advisor: \cvlink{https://scholar.google.it/citations?user=FI1rYesAAAAJ}{Yannis Velegrakis}}

\cventry{2012--2014}
  {Master of Science in Computer Science}
  {University of Trento}{Italy}
  % {\textit{102/110}}
  {}
  {}

\cventry{2009--2012}
  {Bachelor of Science in Computer Science}
  {University of Trento}{Italy}
  % {\textit{97/110}}
  {}
  {}


%************************************************
%************************************************
% \section{Work Experience}
%************************************************
%************************************************

%************************************************
%************************************************
\section{Skills}
%************************************************
%************************************************

\cvlanguage{Programming}{Python · Java · Scala · C\# · SQL (Postgres, MySQL) · Javascript · PHP}{}
\cvlanguage{Big Data}{Apache Spark · Apache Flink · Apache Kafka · Apache Hadoop · NoSQL}{}
\cvlanguagesplit{Certifications}
  {\cvlink{https://s3.amazonaws.com/verify.edx.org/downloads/2436694a40764beab0a6cfe5bb71c7d7/Certificate.pdf}{Scalable Machine Learning with Apache Spark}
   · \cvlink{https://www.udemy.com/certificate/UC-179b7091-1bc8-4248-9f13-ad0c4793488c/}{Python Bootcamp for Data Science 2021}
   · \\ \cvlink{https://www.udemy.com/certificate/UC-050fcde9-af9c-4d52-b995-5d1aff28ff7c/}{Machine Learning Real World Projects in Python}
   · \cvlink{https://www.udemy.com/certificate/UC-0a0116b5-bf40-4dd1-9b6e-32698f19c9ba/}{Machine Learning \& Deep Learning in Python \& R}
   · \\ \cvlink{https://www.udemy.com/certificate/UC-f55283fa-6b09-43f4-9534-39c960b41cc8/}{Deep Learning: GANs and Variational Autoencoders}
  % \cvlink{https://www.eduonix.com/certificate/226aa24a87}{Data Wrangling and Data Visualization in R}
  % \cvlink{https://www.eduonix.com/certificate/92716164e9}{Beginners Guide to Test Driven Development}
  % \cvlink{https://www.udemy.com/certificate/UC-5b6bb1e8-aef0-4c62-b552-20fd583e8c5a/}{Become Agile with Scrum by Examples}
  }
  {}
\cvlanguage{Tools \& OS}{Bash · Git · QGIS · Linux · Mac OS · Windows}{}
\cvlanguage{AI}{Machine Learning · Data Mining}{}


%************************************************
%************************************************
\section{Teaching, Lectures, and Talks}
%************************************************
%************************************************

\cventry{2021}
  {Lecturer, \textit{Apache Spark - The Art of Distributing}}
  {University of Trento}
  {Trento}{Italy}
  {Lecture and lab sessions on Apache Hadoop and Spark for the \textit{Data Mining} M.Sc. course.} %  Reference: \cvlink{https://scholar.google.it/citations?user=FI1rYesAAAAJ}{Yannis Velegrakis}}


\cventry{2021}
  {Invited Talk, \textit{Apache Spark - Notions and Lab Session}}
  {Utrecht University}
  {Utrecht}{The Netherlands}
  {Talk and lab sessions on Apache Hadoop and Spark for the \textit{Data Intensive} M.Sc. course.} %  Reference: \cvlink{https://scholar.google.it/citations?user=FI1rYesAAAAJ}{Yannis Velegrakis}}

\cventry{2020}
  {Invited Talk, \textit{From Hadoop to Spark - A Big Data Journey}}
  {University of Trento}
  {Trento}{Italy}
  {Talk about Big Data tools, with focus on Apache Hadoop and Spark with its libraries.} % Reference: \cvlink{https://scholar.google.it/citations?user=FI1rYesAAAAJ}{Yannis Velegrakis}}

\cventry{2015--2019}
  {Teaching Assistant, \textit{Big Data and Social Networks} course}
  {University of Trento}
  {Trento}{Italy}
  {M.Sc. course on Big Data storage (NoSQL, HDFS) and analysis (MapReduce, Spark, ML models, Streaming, Graph processing), with Data Mining notions. Professor: \cvlink{https://scholar.google.it/citations?user=FI1rYesAAAAJ}{Yannis Velegrakis}}

\cventry{2017}
  {Lecturer, \textit{Big Data for Data Scientists}}
  {Telecom Italia - TIM}
  {Trento}{Italy}
  {Specialized course for the data scientists working at TIM on HDFS, Spark, ML, and Streaming.} %  Reference: \cvlink{https://www.linkedin.com/in/michele-vescovi/}{Michele Vescovi}}

\cventry{2015--2016}
  {Teaching Assistant, \textit{Programming for Mathematicians} course}
  {University of Trento}
  {Trento}{Italy}
  {B.Sc. course for introducing Math students to programming. Professor: \cvlink{https://scholar.google.it/citations?user=ojru0uEAAAAJ}{Roberto Zunino}}


%************************************************
%************************************************
% \section{Invited Talks}
%************************************************
%************************************************

% \cventry{2021}{Invited Talk, Apache Spark - Notions and Lab Session}{Utrecht University}{Utrecht}{The Netherlands}
  % {Talk and lab session for the Data Intensive Course about Apache Hadoop and, in particular, Apache Spark and its libraries, with lab exercises, demo, and practical showcases.\\
   % Reference: \cvlink{https://scholar.google.it/citations?user=FI1rYesAAAAJ}{Yannis Velegrakis}}

% \cventry{2020}{Invited Talk, A Big Data journey}{University of Trento}{Trento}{Italy}
  % {Talk about Big Data tools, with a particular focus on Apache Hadoop and an in-depth analysis of Apache Spark and its libraries.\\
   % Reference: \cvlink{https://scholar.google.it/citations?user=FI1rYesAAAAJ}{Yannis Velegrakis}}


%************************************************
%************************************************
\section{Selected Publications}
%************************************************
%************************************************
\cvpublication{2021}
  {Estimating the Extent of the Effects of Data Quality through Observations}{ICDE 2021}
  {\danieleauthor, M. Lissandrini, and Y. Velegrakis}
  {\hspace{-50pt}\doilink{https://doi.org/10.1109/ICDE51399.2021.00176}{doi:10.1109/ICDE51399.2021.00176}}

\cvpublication{2021}
  {The F4U System for Understanding the Effects of Data Quality}{ICDE 2021}
  {\danieleauthor, M. Lissandrini, and Y. Velegrakis}
  {\hspace{-50pt}\doilink{https://doi.org/10.1109/ICDE51399.2021.00312}{doi:10.1109/ICDE51399.2021.00312}}

\cvpublication{2021}
  {OBELISC: Oscillator-Based Modelling and Control using Efficient Neural Learning for Intelligent Road Traffic Signal Calculation}{ECML-PKDD 2021}
  {C. Axenie, \danieleauthor, A. Wieder, M. Al Hajj Hassan, P. Sottovia, M. Grossi, \dots, S. Bortoli, and G. Brasche}
  % {C. Axenie, \danieleauthor, A. Wieder, M. Al Hajj Hassan, P. Sottovia, M. Grossi, R. Shi, S. Bortoli, and G. Brasche}
  {\hspace{-50pt}\doilink{https://doi.org/10.1007/978-3-030-86514-6\_27}{doi:10.1007/978-3-030-86514-6\_27}}

\cvpublication{2021}
  {TRAMESINO: Traffic Memory System for Intelligent Optimization of Road Traffic Control}{AALTD 2021}
  {C. Axenie, \danieleauthor, A. Wieder, M. Al Hajj Hassan, P. Sottovia, M. Grossi, \dots, S. Bortoli, and G. Brasche}
  % {C. Axenie, \danieleauthor, A. Wieder, M. Al Hajj Hassan, P. Sottovia, M. Grossi, R. Shi, S. Bortoli, and G. Brasche}
  {Av. upon request}

\cvpublication{2020}
  {Real-time Traffic Jam Detection and Congestion Reduction Using Streaming Graph Analytics}{BSD 2020}
  {Z. Abbas, P. Sottovia, M. Al Hajj Hassan, \danieleauthor, S. Bortoli}
  {\hspace{-50pt}\doilink{https://doi.org/10.1109/BigData50022.2020.9378068}{doi:10.1109/BigData50022.2020.9378068}}

\cvpublication{2018}
  {Moira: A Goal-Oriented Incremental Machine Learning Approach to Dynamic Resource Cost Estimation in Distributed Stream Processing Systems}{BIRTE 2018}
  {\danieleauthor, C. Axenie, S. Bortoli, M. Al Hajj Hassan, \dots, and Y. Velegrakis}
  % {\danieleauthor, C. Axenie, S. Bortoli, M. Al Hajj Hassan, R. Acker, R. Tudoran, G. Brasche, and Y. Velegrakis}
  {\hspace{-20pt}\doilink{https://doi.org/10.1145/3242153.3242160}{doi:10.1145/3242153.3242160}}

\cvpublication{2018}
  {STARLORD: Sliding Window Temporal Accumulate-Retract Learning for
Online Reasoning on Datastreams}{ICMLA 2018}
  {C. Axenie, R. Tudoran, S. Bortoli, M. Al Hajj Hassan, \danieleauthor, and G. Brasche}
  {\hspace{-20pt}\doilink{https://doi.org/10.1109/ICMLA.2018.00181}{doi:10.1109/ICMLA.2018.00181}}

\cvpublication{2018}
  {Data Management and Smart Cities}{IEEE Smart Cities 2018}
  {M. Brugnara, C. Consonni, \danieleauthor, S. Pasupathipillai, G. Preti, P. Sottovia, and Y. Velegrakis}
  {\doilink{https://smartcities.ieee.org/images/files/pdf/2019-01_SCWhitePaper-DataManagementinSC.pdf}{White Paper}}
  % {\doilink{https://event.unitn.it/smartcities-trento/Trento_WP_Brugnara1.pdf}{UniTN - White Paper '18}}


%************************************************
%************************************************
\section{Projects}
%************************************************
%************************************************

\cventry{2019--\emph{Now}}{Data Quality Measurement}{Ongoing work}{}{}
  {Built the theoretical framework for assessing the dataset quality for the application (task) the user has in mind. This approach is being applied by big companies and additionally it has bee extensively tested with multiple tasks and datasets.}

\cventry{2020--\emph{Now}}{Entity Matching through data profiling}{Ongoing work}{}{}
  {Exploited the intrinsic value of the data through a profile for improving the accuracy of the duplicates found.}

\cventry{2017}{Data Lake analysis: SQL, statistics, Data Mining, and ML techniques}{Industrial project}{}{}
  {Design a flow of Data Mining and Machine Learning algorithms, combined with statistics and queries defined by the users, to show the key insights from the data.}


% %************************************************
% %************************************************
\section{Awards and Leadership}
% %************************************************
% %************************************************

\cvitemwithcomment{2021}{\textbf{Huawei Year Award.} I got the yearly award for the exceptional work in the previous year.}{}
\cvitemwithcomment{2018--\emph{Now}}{\textbf{Student guidance.} I guided Master and Ph.D. students during their internships.}{}
\cvitemwithcomment{2019}{\textbf{Soccer Data Challenge.} 1\textsuperscript{st} place at the \cvlink{https://www.sobigdata-soccerchallenge.it/trento/}{SoBigData Challenge} about soccer Match Analysis.}{}
\cvitemwithcomment{2015}{\textbf{Travel Awards.} Databricks grant based on the research proposal and achievement.}{}

%************************************************
%************************************************
\section{Other activities}
%************************************************
%************************************************

\cvitemwithcomment{PC member}{EDBT 2021 · SEA Data 2021 · SEA Data 2020}{}
\cvlanguagesplit{Reviewer}{VLDB · ICDE · KDD · SIGMOD Record · IEEE BigData · EDBT · ECML-PKDD · JPDC · ICMLA · CSGRID}{}


%************************************************
%************************************************
\section{Languages}
%************************************************
%************************************************

\cvitemwithcomment{}{\textbf{English:} Full professional proficiency (C1) · \textbf{German:} Basic Knowledge (A1) · \textbf{Italian:} Native}{}
% \cvitemwithcomment{English}{Full professional proficiency (C1)}{}
% \cvitemwithcomment{German}{Basic knowledge (A1)}{}
% \cvitemwithcomment{Italian}{Native}{}


\thispagestyle{plain} % Add footer
\end{document}
